---
title: "Varin patent"
output: html_document
date: "2024-04-01"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## 2023-03-05 Bakker varin genes


## KR gene
Varin genes [116] (p. 34 or p. 35)

Seq ID NO: 1
Seq ID NO: 2 (protein)


[174]


```{r}
# library(ape)
# dna <- read.FASTA("/media/knausb/Vining_lab/public_databases/NCBI/Abacus/GCA_025232715.1/GCA_025232715.1_Csat_AbacusV2_genomic.fna")
# my_seq <- as.matrix(dna[4])[, 72696599:72691998]
# toupper(paste(as.character(my_seq[1:80]), collapse = ""))
```

```
"GTACCGACGGTAACGACCTAGTTTGCAACATCAAAGGTTTAGTTGGTCTTAAAGGTCGAGTAAGAAACTGGCCTTTCGGG"
```




```
>XM_030642595.1 PREDICTED: Cannabis sativa 3-oxoacyl-[acyl-carrier-protein] redu
ctase 4 (LOC115714062), mRNA
ctcctttgggttccgtcgtcaaagatgtacgaacactcttcggagtttccaaagtcccaa
tatataaaaaccaacgtaaacacgaaaaggaacagttcaatttcttatctgggttttcta
aaaactctgcctttttctttgtacaaagcccacaacaatcttcggaactatatatcccat
ggctgccattgctggatcaaacgttgtagtttccaaatcaaccagaatttccagctcatt
ctttgaccggaaagccccacattttcggcagtggtcccccatttccggtggccaatcact
ccgtcactccatctcccttcaatgcaaatccaagagttcctccggtggtgttgttaaagc
tcagggagcaagtcttgaagaaacaagcgccggagtaggccaaaatgtggaggctccggt
ggtcattgtgactggtgcctctagaggtattggaaaagctactgcattggctttgggaaa
agctggttgtaaggtccttgttaattatgctagatcatcaaaggaggctgaggaagtttc
caaagagatcgaagcatctggtggccaagctattacttttggaggagatgtttcaaaaga
agctgatgttgaattaatgatcaaaacagcagttgatgcttggggaactattgatgtatt
agtaaataatgcaggaatcacaagggacaacttaattatgagaatgaagaaatcccagtg
gcaggatgtcattgatttgaatcttactggtgtatttctatgtacacaggctgcagccaa
aattatgatgaagaagaaaaagggaaggataatcaatgtagcatcagtcttcggtctagt
cggcaatgccgggcaagccaattatagtgctgcaaaagcaggagtaattggcttcacaaa
agctattgctaaggagtattccagcagaaacatcactgttaatgctattgctccaggctt
tattgcatctgacatgactgccaagctaggagatgatattgagaagaaaaacttggaggg
catccccttaggaagatatggtcaaccagaagaagttgctgggctagtggaatttttggc
acttggtcctgctgcaagttacataactggacaggttctcaccattgatggagggatggt
aatgtaggccaccctccctgcataattgaggagcctctaaactaccaccaataacaaagc
aatgagaatggtgtaatatccatttttttaaggaaaaaaaaaataagaatttaattctat
ttttacttccatttatttttttttcattttagtattttgaatattgtgaattaaggattt
taatgacaaataaattttatttta
```
**Listing X.** CBDRx LOC115714062, a homolog of Abacus CsaAba2 "KR" (chr4:72696599-72691998).



```
>XP_030498455.1 3-oxoacyl-[acyl-carrier-protein] reductase 4 [Cannabis sativa]
MAAIAGSNVVVSKSTRISSSFFDRKAPHFRQWSPISGGQSLRHSISLQCKSKSSSGGVVKAQGASLEETSAGVGQNVEAP
VVIVTGASRGIGKATALALGKAGCKVLVNYARSSKEAEEVSKEIEASGGQAITFGGDVSKEADVELMIKTAVDAWGTIDV
LVNNAGITRDNLIMRMKKSQWQDVIDLNLTGVFLCTQAAAKIMMKKKKGRIINVASVFGLVGNAGQANYSAAKAGVIGFT
KAIAKEYSSRNITVNAIAPGFIASDMTAKLGDDIEKKNLEGIPLGRYGQPEEVAGLVEFLALGPAASYITGQVLTIDGGM
VM
```
**Listing X.** Seq ID NO: 2 (protein): CBDRx_XP_030498455.faa


The KR gene pt/mtKR/FabG1 (beta ketoacyl-acyl carier protein (ACP) reductase, At1g24360) is also referred to as 3-oxoacyl-[acyl-carrier-protein] reductase.







## 2024-03-05 Bakker varin markers

https://ppubs.uspto.gov/dirsearch-public/print/downloadPdf/11920187

https://patentimages.storage.googleapis.com/c7/48/ce/a3255317acac63/WO2023015268A1.pdf

https://www.ncbi.nlm.nih.gov/nuccore/?term=ketoacyl-acyl+carrier+protein+reductase



Varinolic cannabinoids



## Notable references

Clarke, R. and Merlin, M., 2016. Cannabis: evolution and ethnobotany. Univ of California Press.
- Growth requirements


de Zeeuw, R.A., Wijsbeek, J., Breimer, D.D., Vree, T.B., van Ginneken, C.A. and van Rossum, J.M., 1972. Cannabinoids with a propyl side chain in cannabis: Occurrence and chromatographic behavior. Science, 175(4023), pp.778-779.


Guan, X., Okazaki, Y., Zhang, R., Saito, K. and Nikolau, B.J., 2020. Dual-localized enzymatic components constitute the fatty acid synthase systems in mitochondria and plastids. Plant Physiology, 183(2), pp.517-529.


Livingston, S.J., Quilichini, T.D., Booth, J.K., Wong, D.C., Rensing, K.H., Laflamme‐Yonkman, J., Castellarin, S.D., Bohlmann, J., Page, J.E. and Samuels, A.L., 2020. Cannabis glandular trichomes alter morphology and metabolite content during flower maturation. The Plant Journal, 101(1), pp.37-56.
- Varin in Purple Kush and Finola



Pavlovic, R., Panseri, S., Giupponi, L., Leoni, V. and Citti, C., 2019. Phytochemical and ecological analysis of two varieties of hemp (Cannabis sativa L.) grown in a mountain environment of Italian Alps. Frontiers in Plant Science, 10, p.470737.
https://doi.org/10.3389/fpls.2019.01265 
- Finola as high varin


Welling, M.T., Liu, L., Raymond, C.A., Kretzschmar, T., Ansari, O. and King, G.J., 2019. Complex patterns of cannabinoid alkyl side-chain inheritance in cannabis. Scientific reports, 9(1), p.11421.

Welling, M.T., Liu, L., Kretzschmar, T., Mauleon, R., Ansari, O. and King, G.J., 2020. An extreme-phenotype genome‐wide association study identifies candidate cannabinoid pathway genes in Cannabis. Scientific Reports, 10(1), p.18643.








