---
title: "Chromosome7"
output:
  html_document:
    code_folding: hide
    toc: true
date: "2024-04-26"
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.align = "center")
knitr::opts_chunk$set(fig.height = 6)
knitr::opts_chunk$set(fig.width = 12)
knitr::opts_chunk$set(warning = FALSE)
```


## BLAST results


```{r}
t1 <- Sys.time()
my_df <- read.table("cannsyn_blast.csv", header = TRUE, sep = ",")
my_df$Sample <- sub("\\.chr.", "", my_df$sseqid)
my_df <- my_df[ my_df$Sample != "SN1v3a", ]
my_df <- my_df[ my_df$Sample != "SN1v3b", ]

my_df$fill <- "#C0C0C066"
my_df$pt_shape <- 24
my_df$color <- "#00000022"
my_df$size <- 2.2
my_cann <- my_df[ my_df$qseqid %in% c("AB212829.1", "AB292682.1", "LY658671.1"), ]
my_cann <- my_cann[my_cann$gaps == 0, ]
my_cann <- my_cann[my_cann$pident >= 98, ]
my_cann$fill[ my_cann$qseqid == "AB212829.1" ] <- "#B22222"
my_cann$fill[ my_cann$qseqid == "AB292682.1" ] <- "#1E90FF"
my_cann$fill[ my_cann$qseqid == "LY658671.1" ] <- "#FFD700"
#table(my_cann$fill)
# my_df[1:3, ]
# table(my_df$qseqid)
# range(my_df$send - my_df$sstart, na.rm = TRUE)
```


## BUSCOs


```{r}
busc <- read.csv("BUSCOchrom7.csv.gz")
#busc[1:3, 1:6]
```

Omit NCBI samples.

```{r}
ncbi <- c("CBDRX.CBDRX.chr7",
"CBDRx.NC_044378.1",
"ABAC.ABAC.chr7",
"Abacus.CM046076.1",
"FIN.FIN.chr7",
"Finola.CM011610.1",
"PK.PK.chr7",
"Purple_Kush.CM010797.2",
"Cannbio.2.CM028020.1",
"jl_Kyirong.CM022973.1")
ncbi <- paste(ncbi, collapse = "|")
busc <- busc[ , grep(ncbi, names(busc), invert = TRUE)]
```


## Chemotype


```{r}
type1 <- c("AH3Ma", "AH3Mb", "COFBa", "COFBb", "DPFBa", "DPFBb", "MBFBa", 
"MBFBb", "NLv1a", "NLv1b", "OFBa", "OFBb", "PPFBa", "PPFBb", 
"SDFBa", "SDFBb", "SKFBa", "SKFBb", "SODLa", "SODLb", "SZFBa", 
"SZFBb", "TKFBa", "TKFBb", "TWFBa", "TWFBb", "UFBa", "UFBb", 
"WCFBa", "WCFBb", "WHWa", "WHWb")
type2 <- c("COSVa", "COSVb", "DPSVa", "DPSVb", "EH23a", "EH23b", "MBSVa", 
"MBSVb", "S8Ha", "S8Hb", "SHH5a", "SHH5b", "STHa", "STHb", "TWSVa", 
"TWSVb")
type3 <- c("BCMa", "BCMb", "BOAXa", "BOAXb", "GERv1a", "GERv1b", "GRMa", 
"GRMb", "KCDv1a", "KCDv1b", "KOMPa", "KOMPb", "MM3v1a", "MM3v1b", 
"SVA12a", "SVA12b", "SVA6a", "SVA6b", "YMv2a", "YMv2b")
type4 <- c("FCS1a", "FCS1b", "H3S1a", "H3S1b", "H3S7a", "H3S7b", "SAN2a", 
"SAN2b")

type1 <- busc[, type1]
type2 <- busc[, type2]
type3 <- busc[, type3]
type4 <- busc[, type4]

inversion <- c("AH3Ma", "OFBa", "SKFBa", "SZFBa", "TKFBa")
inversion <- paste(inversion, collapse = "$|^")

#type1 <- type1[, c(grep(inversion, colnames(type1)), grep(inversion, colnames(type1), invert = TRUE))]
type1 <- type1[, c(grep(inversion, colnames(type1), invert = TRUE),
                   grep(inversion, colnames(type1), invert = FALSE))]

my_breaks <- ncol(type1)
my_breaks <- c(my_breaks, my_breaks[length(my_breaks)] + ncol(type2))
my_breaks <- c(my_breaks, my_breaks[length(my_breaks)] + ncol(type3))
my_breaks <- c(my_breaks, my_breaks[length(my_breaks)] + ncol(type4))
my_breaks <- my_breaks + 0.5

#gg_line_map(type1, check_table = FALSE)
busc <- cbind(type1, type2, type3, type4)
```



```{r}
library(BUSCOplot)
library(ggplot2)
#p <- gg_line_map(busc, check_table = FALSE)
p <- gg_line_map(busc, palpha = 0.2, size = 1.4, 
                 lalpha = 0.12, linewidth = 0.8,
                 check_table = FALSE)

p <- p + geom_vline(xintercept = my_breaks)
lheight <- 69e6
p <- p + annotate( geom = "label",
                   x = 20, y = lheight,
                   label = "THCAS\nChemotype I")
p <- p + annotate( geom = "label",
              x = my_breaks[1] + (my_breaks[2] - my_breaks[1])/2,
              y = lheight,
              label = "THCAS:CBDAS\nChemotype II")
p <- p + annotate( geom = "label",
              x = my_breaks[2] + (my_breaks[3] - my_breaks[2])/2,
              y = lheight,
              label = "CBDAS\nChemotype III")
p <- p + annotate( geom = "label",
              x = my_breaks[3] + (my_breaks[4] - my_breaks[3])/2,
              y = lheight,
              label = "IV")

p <- p + annotate( geom = "point",
              x = my_df$Sample,
              #x = as.numeric(my_df$Sample),
              y = my_df$sstart,
              fill = my_df$fill,
              shape = my_df$pt_shape,
              color = my_df$color,
              size = my_df$size)

p <- p + annotate( geom = "point",
              x = my_cann$Sample,
              #x = as.numeric(my_cann$Sample),
              y = my_cann$sstart,
              fill = my_cann$fill,
              shape = my_cann$pt_shape,
              color = my_cann$color,
              size = my_cann$size)


p
```


The elevation of points represent the position of BUSCO genes along each chromosome, where colored lines connect identical BUSCO genes occurring in neighboring chromosomes.
Three colors of triangles mark the location of sequences similar to CBCAS, CBDAS, or THCAS based on a BLASTN query.
Gray triangles mark a low stringency match (percent identity greater than 90%) for all three synthases.
Firebrick red triangles mark a high stringency match (percent identity greater than 98%, zero gaps) for THCAS (AB212829.1).
Dodger blue triangles mark a high stringency match (percent identity greater than 98%, zero gaps) for CBDAS (AB292682.1).
Gold triangles mark a high stringency match (percent identity greater than 98%, zero gaps) for CBCAS (AB292682.1).



## Zero on BUSCO_ID=127689at71240


```{r, fig.cap="**Figure X.** BUSCO line map."}
#format(sort(tmp[, 1]), big.mark = ",")

my_min <- busc["BUSCO_ID=127689at71240", ] # 8,913,442
#my_min <- tmp["BUSCO_ID=100415at71240", ] # 12,051,090

my_min <- as.vector(my_min, mode = "numeric")
names(my_min) <- colnames(busc)

#my_min[ is.na(my_min) ]
my_min[ is.na(my_min) ] <- mean(as.numeric(my_min), na.rm = TRUE)

all(names(my_min) == colnames(busc))

busc <- sweep(busc, MARGIN = 2, STATS = as.numeric(my_min), FUN = "-")

my_df$sstart <- my_df$sstart - my_min[my_df$Sample]
my_cann$sstart <- my_cann$sstart - my_min[my_cann$Sample]

#my_df$Sample <- factor(my_df$Sample, levels = colnames(tmp))

p <- gg_line_map(busc, palpha = 0.2, size = 1.4, 
                 lalpha = 0.12, linewidth = 0.8,
                 check_table = FALSE)

p <- p + annotate( geom = "point",
              x = my_df$Sample,
              #x = as.numeric(my_df$Sample),
              y = my_df$sstart,
              fill = my_df$fill,
              shape = my_df$pt_shape,
              color = my_df$color,
              size = my_df$size)

p <- p + annotate( geom = "point",
              x = my_cann$Sample,
              #x = as.numeric(my_cann$Sample),
              y = my_cann$sstart,
              fill = my_cann$fill,
              shape = my_cann$pt_shape,
              color = my_cann$color,
              size = my_cann$size)

#p <- p + theme(axis.text.x = element_text( color = tick_col ))

p <- p + geom_vline(xintercept = my_breaks)

#lheight <- 72e6
#lheight <- 70e6
lheight <- 69e6
p <- p + annotate( geom = "label",
                   x = 20, y = lheight,
                   label = "THCAS\nChemotype I")
p <- p + annotate( geom = "label",
              x = my_breaks[1] + (my_breaks[2] - my_breaks[1])/2,
              y = lheight,
              label = "THCAS:CBDAS\nChemotype II")
p <- p + annotate( geom = "label",
              x = my_breaks[2] + (my_breaks[3] - my_breaks[2])/2,
              y = lheight,
              label = "CBDAS\nChemotype III")
p <- p + annotate( geom = "label",
              x = my_breaks[3] + (my_breaks[4] - my_breaks[3])/2,
              y = lheight,
              label = "IV")
#p
```



## Zoom on y-axis, zero on BUSCO_ID=127689at71240


```{r, fig.cap="BUSCO line map, y-axis zeroed on BUSCO_ID=127689at71240."}

#p + ylim(-1.4e6, 5e6)
#p + ylim(0, 4e6) #+ scale_y_discrete( breaks = seq(0, 4e6, by = 1e6), labels = seq(0, 4, by = 1))

p2 <- p + scale_y_continuous( breaks = seq(-1e9, 1e9, by = 1e6),
                        labels = seq(-1e9, 1e9, by = 1e6)/1e6,
                        minor_breaks = seq(-1e9, 1e9, by = 0.5e6), 
                        limits = c(0, 4.1e6) )
#                        limits = c(0, 4.2e6) )

lheight <- 4e6
p2 <- p2 + annotate( geom = "label",
                   x = 20, y = lheight,
                   label = "THCAS\nChemotype I")
p2 <- p2 + annotate( geom = "label",
              x = my_breaks[1] + (my_breaks[2] - my_breaks[1])/2,
              y = lheight,
              label = "THCAS:CBDAS\nChemotype II")
p2 <- p2 + annotate( geom = "label",
              x = my_breaks[2] + (my_breaks[3] - my_breaks[2])/2,
              y = lheight,
              label = "CBDAS\nChemotype III")
p2 <- p2 + annotate( geom = "label",
              x = my_breaks[3] + (my_breaks[4] - my_breaks[3])/2,
              y = lheight,
              label = "IV")

p2 <- p2 + annotate( geom = "text",
              x = 16,
              y = 2e5,
              size = 2.8,
              label = "BUSCO: 127689at71240")

p2 <-p2 + annotate( geom = 'point', x = rep(78, times = 4),
               xmax = 80, 
               #y = c(1.0e6, 2e6, 3.0e6),
               y = c(1.0e6, 2e6, 3.0e6, 4.0e6),
               size = 4, pch = 24, 
               bg = c("#C0C0C066", "#B22222","#1E90FF", "#FFD700"))
p2 <- p2 + annotate( geom = 'text', x = rep(78, times = 4), 
                     y = c(0.8e6, 1.8e6, 2.8e6, 3.8e6) - 0.2e6, 
                     label = c("CanSyn", "THCAS", "CBDAS", "CBCAS"), 
                     size = 4, angle = -90 )
p2 <- p2 + theme(axis.text.x = element_text( size = 6 ))
#p2 <- p2 + theme(axis.text.x = element_text( size = 8 ))

p2

# ggsave(filename = "BUSCOlineplot_zerozoom.png", device = "png",
#        width = 6.5,
# #       width = 4.5,
#        height = 4.5, units = "in", dpi = 300)

```




```{r}
t99 <- Sys.time()
t99 - t1
```


